Response to reviewers

### 2025-01-23 Manuscript/Tables/results_differences2d_2.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_1 & FA.ses\_1 & FA.d\_2 & FA.ses\_2 & FA.d\_3 & FA.ses\_3 & FA.d\_4 & FA.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 34.1*** & 1.51 & 32.08*** & 1.19 & 32.28*** & 1.14 & 28.07*** & 0.98 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 21.27*** & 1.29 & 18.72*** & 1.03 & 17.59*** & 0.96 & 14.25*** & 0.77 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 21.81*** & 1.94 & 21.56*** & 1.56 & 22.13*** & 1.53 & 19.58*** & 1.33 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 22.76*** & 2.2 & 26.13*** & 1.63 & 29.21*** & 2.18 & 24.35*** & 1.85 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0 & -0.03 & 0 & 0.1 & -0.01** & -0.16 & -0.01*** & -0.2 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.76*** & 1.12 & 0.6*** & 0.89 & 0.55*** & 0.82 & 0.46*** & 0.69 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.08*** & 0.77 & 0.06*** & 0.59 & 0.05*** & 0.47 & 0.03*** & 0.33 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.88*** & 3.28 & 0.7*** & 3.57 & 0.6*** & 4.16 & 0.44*** & 4.18 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.02*** & 0.61 & 0.01*** & 0.53 & 0.01*** & 0.31 & 0 & -0.09 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.09*** & -1.01 & -0.06*** & -0.84 & -0.05*** & -0.81 & -0.04*** & -0.73 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0** & 0.35 & 0 & 0.09 & 0*** & -0.24 & 0*** & -0.45 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.25*** & 5.31 & 0.15*** & 3.43 & 0.06*** & 2.12 & -0.01*** & -0.45 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:47 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_rm1 & FA.ses\_rm1 & FA.d\_rm2 & FA.ses\_rm2 & FA.d\_rm3 & FA.ses\_rm3 & FA.d\_rm4 & FA.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 34.1*** & 1.51 & 32.08*** & 1.19 & 32.28*** & 1.14 & 28.07*** & 0.98 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 21.27*** & 1.29 & 18.72*** & 1.03 & 17.59*** & 0.96 & 14.25*** & 0.77 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 21.81*** & 1.94 & 21.56*** & 1.56 & 22.13*** & 1.53 & 19.58*** & 1.33 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 22.76*** & 2.2 & 26.13*** & 1.63 & 29.21*** & 2.18 & 24.35*** & 1.85 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0 & -0.03 & 0 & 0.1 & -0.01** & -0.16 & -0.01*** & -0.2 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.76*** & 1.12 & 0.6*** & 0.89 & 0.55*** & 0.82 & 0.46*** & 0.69 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.08*** & 0.77 & 0.06*** & 0.59 & 0.05*** & 0.47 & 0.03*** & 0.33 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.88*** & 3.28 & 0.7*** & 3.57 & 0.6*** & 4.16 & 0.44*** & 4.18 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.02*** & 0.61 & 0.01*** & 0.53 & 0.01*** & 0.31 & 0 & -0.09 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.09*** & -1.01 & -0.06*** & -0.84 & -0.05*** & -0.81 & -0.04*** & -0.73 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0** & 0.35 & 0 & 0.09 & 0*** & -0.24 & 0*** & -0.45 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.25*** & 5.31 & 0.15*** & 3.43 & 0.06*** & 2.12 & -0.01*** & -0.45 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FA = FA; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences2d_3.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_1 & FI.ses\_1 & FI.d\_2 & FI.ses\_2 & FI.d\_3 & FI.ses\_3 & FI.d\_4 & FI.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 44.79*** & 2.45 & 42.48*** & 1.98 & 36.94*** & 1.58 & 25.79*** & 1.08 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 31.28*** & 2.26 & 27.45*** & 1.85 & 22.78*** & 1.45 & 14.93*** & 0.95 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 28.59*** & 3.14 & 28.96*** & 2.67 & 26.06*** & 2.22 & 18.98*** & 1.58 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 21.29*** & 3.08 & 24.42*** & 2.89 & 22.75*** & 2.08 & 15.6*** & 1.39 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.04*** & 0.95 & 0.01 & 0.14 & -0.01** & -0.26 & -0.02*** & -0.41 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 1.27*** & 2.4 & 1.03*** & 1.88 & 0.81*** & 1.48 & 0.53*** & 0.98 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.14*** & 1.34 & 0.09*** & 0.92 & 0.06*** & 0.62 & 0.03*** & 0.33 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 1.2*** & 4.88 & 0.99*** & 5.02 & 0.78*** & 4.56 & 0.49*** & 4.4 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.06*** & 2.38 & 0.04*** & 1.71 & 0.03*** & 1.1 & 0.01*** & 0.46 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.05*** & -0.71 & -0.02*** & -0.4 & -0.01*** & -0.23 & 0 & -0.07 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0* & 0.25 & 0. & 0.17 & 0 & 0.11 & 0 & -0.03 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.02*** & 0.46 & 0.01*** & 0.34 & 0 & -0.03 & 0*** & -0.2 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:50 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FI.d\_rm1 & FI.ses\_rm1 & FI.d\_rm2 & FI.ses\_rm2 & FI.d\_rm3 & FI.ses\_rm3 & FI.d\_rm4 & FI.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 44.79*** & 2.45 & 42.48*** & 1.98 & 36.94*** & 1.58 & 25.79*** & 1.08 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 31.28*** & 2.26 & 27.45*** & 1.85 & 22.78*** & 1.45 & 14.93*** & 0.95 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 28.59*** & 3.14 & 28.96*** & 2.67 & 26.06*** & 2.22 & 18.98*** & 1.58 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 21.29*** & 3.08 & 24.42*** & 2.89 & 22.75*** & 2.08 & 15.6*** & 1.39 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.04*** & 0.95 & 0.01 & 0.14 & -0.01** & -0.26 & -0.02*** & -0.41 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 1.27*** & 2.4 & 1.03*** & 1.88 & 0.81*** & 1.48 & 0.53*** & 0.98 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.14*** & 1.34 & 0.09*** & 0.92 & 0.06*** & 0.62 & 0.03*** & 0.33 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 1.2*** & 4.88 & 0.99*** & 5.02 & 0.78*** & 4.56 & 0.49*** & 4.4 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.06*** & 2.38 & 0.04*** & 1.71 & 0.03*** & 1.1 & 0.01*** & 0.46 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.05*** & -0.71 & -0.02*** & -0.4 & -0.01*** & -0.23 & 0 & -0.07 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0* & 0.25 & 0. & 0.17 & 0 & 0.11 & 0 & -0.03 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.02*** & 0.46 & 0.01*** & 0.34 & 0 & -0.03 & 0*** & -0.2 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FI = FI; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences2d_4.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_1 & CO.ses\_1 & CO.d\_2 & CO.ses\_2 & CO.d\_3 & CO.ses\_3 & CO.d\_4 & CO.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 17.17*** & 0.79 & 18.21*** & 0.76 & 16.88*** & 0.68 & 12.58*** & 0.48 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 13.24*** & 0.89 & 14.64*** & 0.96 & 12.41*** & 0.81 & 9.06*** & 0.57 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 11.24*** & 1.1 & 12.26*** & 1.05 & 11.73*** & 0.95 & 8.88*** & 0.67 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 7.71*** & 1.17 & 11*** & 1.24 & 11.32*** & 1.14 & 8.68*** & 0.74 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.04*** & 0.87 & 0.04*** & 1.01 & 0.03*** & 0.72 & 0.02*** & 0.49 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.51*** & 0.9 & 0.51*** & 0.93 & 0.41*** & 0.77 & 0.31*** & 0.56 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.06*** & 0.58 & 0.05*** & 0.52 & 0.04*** & 0.4 & 0.03*** & 0.26 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.71*** & 3.18 & 0.67*** & 4.05 & 0.53*** & 4.31 & 0.36*** & 3.85 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.04*** & 1.3 & 0.04*** & 1.73 & 0.03*** & 1.25 & 0.02*** & 0.83 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.02** & -0.29 & -0.01. & -0.13 & 0 & -0.08 & 0 & -0.01 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0** & 0.32 & 0*** & 0.35 & 0*** & 0.3 & 0*** & 0.19 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.03*** & 0.76 & 0.03*** & 0.99 & 0.01*** & 0.62 & 0.01*** & 0.32 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:52 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & CO.d\_rm1 & CO.ses\_rm1 & CO.d\_rm2 & CO.ses\_rm2 & CO.d\_rm3 & CO.ses\_rm3 & CO.d\_rm4 & CO.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 17.17*** & 0.79 & 18.21*** & 0.76 & 16.88*** & 0.68 & 12.58*** & 0.48 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 13.24*** & 0.89 & 14.64*** & 0.96 & 12.41*** & 0.81 & 9.06*** & 0.57 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 11.24*** & 1.1 & 12.26*** & 1.05 & 11.73*** & 0.95 & 8.88*** & 0.67 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 7.71*** & 1.17 & 11*** & 1.24 & 11.32*** & 1.14 & 8.68*** & 0.74 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.04*** & 0.87 & 0.04*** & 1.01 & 0.03*** & 0.72 & 0.02*** & 0.49 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.51*** & 0.9 & 0.51*** & 0.93 & 0.41*** & 0.77 & 0.31*** & 0.56 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.06*** & 0.58 & 0.05*** & 0.52 & 0.04*** & 0.4 & 0.03*** & 0.26 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.71*** & 3.18 & 0.67*** & 4.05 & 0.53*** & 4.31 & 0.36*** & 3.85 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.04*** & 1.3 & 0.04*** & 1.73 & 0.03*** & 1.25 & 0.02*** & 0.83 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.02** & -0.29 & -0.01. & -0.13 & 0 & -0.08 & 0 & -0.01 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0** & 0.32 & 0*** & 0.35 & 0*** & 0.3 & 0*** & 0.19 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.03*** & 0.76 & 0.03*** & 0.99 & 0.01*** & 0.62 & 0.01*** & 0.32 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D).CO = CO; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences4d_1.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_1 & EQ.ses\_1 & EQ.d\_2 & EQ.ses\_2 & EQ.d\_3 & EQ.ses\_3 & EQ.d\_4 & EQ.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 1024.68*** & 2.29 & 1305.5*** & 1.94 & 1221.81*** & 1.37 & 794.58*** & 0.74 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 2277.38*** & 2.33 & 2433.1*** & 2.04 & 2101.05*** & 1.48 & 1349.76*** & 0.84 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 449.97*** & 3.43 & 720.41*** & 3.62 & 780.96*** & 2.77 & 628.64*** & 1.8 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 42.72*** & 4.14 & 51.54*** & 3.7 & 46.87*** & 2.64 & 30.12*** & 1.5 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.13*** & 3.66 & 0.07*** & 1.91 & 0.03*** & 0.92 & 0.01*** & 0.16 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 2*** & 3.53 & 1.65*** & 2.84 & 1.25*** & 2.06 & 0.78*** & 1.23 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.16*** & 1.76 & 0.11*** & 1.25 & 0.08*** & 0.88 & 0.04*** & 0.52 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 4.19*** & 15.4 & 2.92*** & 15.04 & 1.97*** & 11.6 & 1.1*** & 8.48 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.01*** & 1.2 & 0*** & 0.37 & 0*** & -0.21 & 0*** & -0.55 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.23*** & -5.95 & -0.14*** & -5.16 & -0.08*** & -4.15 & -0.04*** & -2.33 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0*** & -0.56 & 0*** & -0.4 & 0*** & -0.49 & 0** & -0.12 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & -0.01** & -0.33 & -0.01*** & -0.68 & -0.01*** & -0.62 & -0.01*** & -0.54 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:55 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_rm1 & EQ.ses\_rm1 & EQ.d\_rm2 & EQ.ses\_rm2 & EQ.d\_rm3 & EQ.ses\_rm3 & EQ.d\_rm4 & EQ.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 1024.68*** & 2.29 & 1305.5*** & 1.94 & 1221.81*** & 1.37 & 794.58*** & 0.74 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 2277.38*** & 2.33 & 2433.1*** & 2.04 & 2101.05*** & 1.48 & 1349.76*** & 0.84 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 449.97*** & 3.43 & 720.41*** & 3.62 & 780.96*** & 2.77 & 628.64*** & 1.8 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 42.72*** & 4.14 & 51.54*** & 3.7 & 46.87*** & 2.64 & 30.12*** & 1.5 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.13*** & 3.66 & 0.07*** & 1.91 & 0.03*** & 0.92 & 0.01*** & 0.16 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 2*** & 3.53 & 1.65*** & 2.84 & 1.25*** & 2.06 & 0.78*** & 1.23 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.16*** & 1.76 & 0.11*** & 1.25 & 0.08*** & 0.88 & 0.04*** & 0.52 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 4.19*** & 15.4 & 2.92*** & 15.04 & 1.97*** & 11.6 & 1.1*** & 8.48 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.01*** & 1.2 & 0*** & 0.37 & 0*** & -0.21 & 0*** & -0.55 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.23*** & -5.95 & -0.14*** & -5.16 & -0.08*** & -4.15 & -0.04*** & -2.33 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0*** & -0.56 & 0*** & -0.4 & 0*** & -0.49 & 0** & -0.12 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & -0.01** & -0.33 & -0.01*** & -0.68 & -0.01*** & -0.62 & -0.01*** & -0.54 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}

### 2025-01-23 Manuscript/Tables/results_differences4d_2.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_1 & FA.ses\_1 & FA.d\_2 & FA.ses\_2 & FA.d\_3 & FA.ses\_3 & FA.d\_4 & FA.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 517.78*** & 0.82 & 783.51*** & 0.96 & 877.91*** & 0.9 & 724.23*** & 0.67 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 940.19*** & 0.71 & 1134.97*** & 0.72 & 1169.29*** & 0.68 & 945.03*** & 0.53 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 235.02*** & 1.11 & 401.13*** & 1.49 & 477.06*** & 1.45 & 439.74*** & 1.23 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 29.27*** & 0.74 & 51.57*** & 1.85 & 57.78*** & 2.4 & 43.32*** & 2.14 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0 & -0.03 & 0 & 0.05 & 0.01*** & 0.21 & 0*** & 0.1 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 0.36*** & 0.47 & 0.4*** & 0.53 & 0.39*** & 0.52 & 0.31*** & 0.43 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.03*** & 0.4 & 0.03*** & 0.37 & 0.03*** & 0.33 & 0.02*** & 0.24 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 0.53*** & 1.38 & 0.62*** & 2.38 & 0.6*** & 3.1 & 0.46*** & 3.63 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.03*** & 2.88 & 0.02*** & 2.69 & 0.02*** & 2.31 & 0.01*** & 0.93 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.03*** & -0.75 & -0.03*** & -1 & -0.03*** & -1.14 & -0.02*** & -0.92 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0. & -0.21 & 0*** & -0.75 & 0*** & -0.52 & 0*** & -0.4 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & 0.22*** & 4.28 & 0.11*** & 3.5 & 0.03*** & 1.38 & -0.01*** & -0.55 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:57 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & FA.d\_rm1 & FA.ses\_rm1 & FA.d\_rm2 & FA.ses\_rm2 & FA.d\_rm3 & FA.ses\_rm3 & FA.d\_rm4 & FA.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 517.78*** & 0.82 & 783.51*** & 0.96 & 877.91*** & 0.9 & 724.23*** & 0.67 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 940.19*** & 0.71 & 1134.97*** & 0.72 & 1169.29*** & 0.68 & 945.03*** & 0.53 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 235.02*** & 1.11 & 401.13*** & 1.49 & 477.06*** & 1.45 & 439.74*** & 1.23 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 29.27*** & 0.74 & 51.57*** & 1.85 & 57.78*** & 2.4 & 43.32*** & 2.14 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0 & -0.03 & 0 & 0.05 & 0.01*** & 0.21 & 0*** & 0.1 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.36*** & 0.47 & 0.4*** & 0.53 & 0.39*** & 0.52 & 0.31*** & 0.43 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.03*** & 0.4 & 0.03*** & 0.37 & 0.03*** & 0.33 & 0.02*** & 0.24 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.53*** & 1.38 & 0.62*** & 2.38 & 0.6*** & 3.1 & 0.46*** & 3.63 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.03*** & 2.88 & 0.02*** & 2.69 & 0.02*** & 2.31 & 0.01*** & 0.93 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.03*** & -0.75 & -0.03*** & -1 & -0.03*** & -1.14 & -0.02*** & -0.92 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0. & -0.21 & 0*** & -0.75 & 0*** & -0.52 & 0*** & -0.4 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & 0.22*** & 4.28 & 0.11*** & 3.5 & 0.03*** & 1.38 & -0.01*** & -0.55 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FA = FA; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}
